### 2014-06-30 tex/pseudo-code.tex
Fixed last of lazy initialization rules

Locations are boxes in the graphical representation and indicated with
the letter $l$ in the math. References are circles in the graphical
representation and indicated with the letter $r$ in the math. Edges
from locations are labeled with field names $f \in F$. Edges from the
references are labeled with constraints $\phi \in \Phi$ (we assume
$\Phi$ is a power set over individual constraints and $\phi$ is a set
of constraints for the edge).

>>>>

Locations are boxes in the graphical representation and indicated with
the letter $l$ in the math. References are circles in the graphical
representation and indicated with the letter $\cfgnt{r}$ in the
math. The special symbol $\bot$ is an uninitialized reference. Edges
from locations are labeled with field names $\cfgnt{f}$. Edges from
the references are labeled with constraints $\phi \in \Phi$ (it is
assumed that $\Phi$ is a power set over individual constraints and
$\phi$ is a set of constraints for the edge).
